Improving the Efficiency of Dislocality Constraints for an Automated Software Mapping in Safety-Critical Systems

### 2017-12-19 paper.tex
Added more text

\subsection{Toolsuite ASSIST}
As a proof of concept for the ongoing research toward an automated construction of deployments based on Constraint Satisfaction Problems, the toolsuite \emph{Architecture Synthesis for Safety-Critical Systems (ASSIST)}~\cite{ASSIST} was developed by the authors.
It is open source and uses the constraint solver \emph{Choco}~\cite{Prudhomme2016} internally.
ASSIST (see Figure~\ref{tool}) allows a systems engineer to automatically construct and optimize mappings and schedules based on textual specifications of the

\begin{itemize}
\item software components and hardware resources,
\item constraints for valid/invalid assignments (\textit{dislocality}, \textit{dissimilarity}, \textit{colocality}) and 
\item optimization goals.
\end{itemize}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\textwidth]{assist-screenshot}
\caption{Screenshot of ASSIST with a specification for a control system}
\label{tool}
\end{figure}

\section{Ensuring Redundancy by Requiring Dislocality}

\begin{itemize}
\item In order to ensure a reliability / redundancy work properly - it is essential to ensure is differences
\item Differences in the deployment of redundant software components to make sure that the errors do not appear in the same manner at the same location (zonal effects)
\item Dislocality is a typical constraint in ASSIST to express these differences
\item Simple Modeling approach for a CSP (location variables)
\item Use allDiffererent constraint - straight forward
\item Reality: AllDifferent for List of Lists
\item Example to describe the differences
\end{itemize}

>>>>

\subsection{Toolsuite ASSIST}

As a proof of concept for the ongoing research toward an automated construction of deployments based on Constraint Satisfaction Problems, the toolsuite \emph{Architecture Synthesis for Safety-Critical Systems (ASSIST)}~\cite{ASSIST} was developed by the authors.
It is publicly available under the Eclipse Public License 2.0 and uses the constraint solver \emph{Choco 4}~\cite{Prudhomme2016} internally.

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{assist-screenshot}
\caption{Screenshot of ASSIST with a specification for a control system}
\label{tool}
\end{figure}

ASSIST (see Figure~\ref{tool}) allows a systems engineer to automatically construct and optimize mappings and schedules based on textual specifications of the

\begin{itemize}
\item software components and hardware resources,
\item \textit{dislocality}, \textit{dissimilarity} and \textit{colocality} requirements,
\item optimization goals.
\end{itemize}

@@

\section{Ensuring Fault Tolerance by Requiring Dislocality}

In order to achieve fault tolerance and reliability, it is essential to support ``significant differences'' in the choice of resources to which critical software components are deployed to.
For instance, a simple redundancy requirement between two software components, may force the systems engineer to allocate these software components to different processing boards in different locations aboard an airplane.
Furthermore, systematic errors and undetected design flaws in hardware components may be addressed by choosing dissimilar hardware resources, for example processors or memory blocks from different vendors.

Due to the importance of choosing  ``different'' resources for fault tolerance and reliability in safety-critical systems, engineering tools for an automated construction of deployments need to be able to fully support these choices.
ASSIST supports the engineer by offering \emph{dislocality} and \emph{dissimilarity} requirements as part of the domain specific language.
They can be used to enforce ``differences'' for the choice of resources for the mapping of software components.
Finding an \emph{efficient} formulation to express the semantics of each requirement as a Constraint Satisfaction Problem is challenging, but also essential in order to provide an effective toolsuite for the engineering of safety-critical systems.

In order to illustrate the challenges and to present specific modeling improvements, the \emph{dislocality} requirement is used as an central example in this paper.
Please note, that the concepts developed for \emph{dislocality} requirements can also be reused for \emph{dissimilarity} requirements.

\begin{itemize}
\item Simple Modeling approach for a CSP (location variables)
\item Use allDiffererent constraint - straight forward
\item Reality: AllDifferent for List of Lists
\item Example to describe the differences
\end{itemize}
